---
title: "Reticulate Set-up - Step By Step"
author: "Evan Canfield"
date: "12/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Reticulate / Python Setup
```{r}
virtualenv_dir = Sys.getenv('VIRTUALENV_NAME')
python_path = Sys.getenv('PYTHON_PATH')

# create New Virtual Environment If First Time
virtualenv_list <-  reticulate::virtualenv_list()

# Create New Virtual Environment if Needed
if (!(virtualenv_dir %in% virtualenv_list)){
  reticulate::virtualenv_create(envname = virtualenv_dir, python = python_path)
}


# Install Packages
PYTHON_DEPENDENCIES = c("numpy", "joblib", "scikit-learn", "fasttext")
PIP_OPTIONS ='pip install --upgrade pip'


reticulate::virtualenv_install(virtualenv_dir, packages = PYTHON_DEPENDENCIES, 
                               ignore_installed=TRUE, pip_options = PIP_OPTIONS)


# Use Python
reticulate::use_virtualenv(virtualenv_dir, required =TRUE)
```


```{r}

```

```{r}
np <- reticulate::import("numpy")
ft <- reticulate::import("fasttext")
joblib <- reticulate::import("joblib")
sklearn  <- reticulate::import("sklearn")
```

# Processing
## Data
We'll import a random pdf from the available dataset to use as our example input.
We built our processing steps around the resultant text from the **Tabulizer** package. We'll convert from pdf to text immediately on the import, and then process this raw text.

We also need to upload our patterns reference, which will be used to remove specific custom patterns.

```{r import_data}
# PDF Input
## Define Path
pdf_path <- "./../data/input_pdfs/afglmm10hrm.pdf"

## Import and Convert to Text
sample <- extract_text(pdf_path)

# Patterns File
patterns_col <- c("remove","comments")
patterns_raw <- read_excel(path = "../data/patterns.xlsx", col_names = patterns_col, )
patterns <- patterns_raw %>% pull(remove)
```

# Pre-Process Steps
## Process Data
With our pdf now converted to text, we'll process this raw text data.
```{r process_data}
text_processed <- process_text(input_text = sample, 
                                  removal_patterns = patterns)
text_processed[0:5]
```

## Extract Hypothesis
```{r extract_hypothesis}
hypo_xtr <- extract_hypothesis(text_processed)
hypo
